---
title: "Benefit Plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(tidyverse)
```

Load results of the simulations (`sim_benefit.R`)

```{r}
f <- list.files("results", pattern = "file", full.names = TRUE)

out <- ldply(f, function(x) get(load(x))) %>% 
  group_by(p_supply, p_demand, f_supply, f_demand, inter, es_thresh, ee_thres, rival, alpha, beta, gamma) %>% 
  summarise(num_supply_mean = mean(num_supply),
            num_supply_sd = sd(num_supply),
            num_demand_mean = mean(num_demand),
            num_demand_sd = sd(num_demand),
            ee_density_mean = mean(ee_density),
            ee_density_sd = sd(ee_density),
            se_density_mean = mean(se_density),
            se_density_sd = sd(se_density),
            benefit_mean = mean(benefit),
            benefit_sd = sd(benefit)) %>% 
  filter(alpha == "1", 
         beta == "0.1", 
         gamma == "0.1")
```

# Low supply (0.1), Low demand (0.1)

```{r}
# calculate scenarios
noneprox <- filter(out, p_supply == 0.1, p_demand == 0.1, is.na(ee_thres), es_thresh == 20)
nonenot <- filter(out, p_supply == 0.1, p_demand == 0.1, is.na(ee_thres), es_thresh == 100)
proxprox <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 20, es_thresh == 20)
proxnot <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 20, es_thresh == 100)
notnot <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 100, es_thresh == 100)
```

## No supply-supply links, proximal supply-demand links
```{r}
ggplot(noneprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## No supply-supply links, full supply-demand links
```{r}
ggplot(nonenot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, proximal supply-demand links
```{r}
ggplot(proxprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, full supply-demand links
```{r}
ggplot(proxnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## Full supply-supply links, full supply-demand links
```{r}
ggplot(notnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

# Low supply (0.1), high demand (0.4)

```{r}
noneprox <- filter(out, p_supply == 0.1, p_demand == 0.4, is.na(ee_thres), es_thresh == 20)
nonenot <- filter(out, p_supply == 0.1, p_demand == 0.4, is.na(ee_thres), es_thresh == 100)
proxprox <- filter(out, p_supply == 0.1, p_demand == 0.4, ee_thres == 20, es_thresh == 20)
proxnot <- filter(out, p_supply == 0.1, p_demand == 0.4, ee_thres == 20, es_thresh == 100)
notnot <- filter(out, p_supply == 0.1, p_demand == 0.4, ee_thres == 100, es_thresh == 100)
```


## No supply-supply links, proximal supply-demand links
```{r}
ggplot(noneprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## No supply-supply links, full supply-demand links
```{r}
ggplot(nonenot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, proximal supply-demand links
```{r}
ggplot(proxprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, full supply-demand links
```{r}
ggplot(proxnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## Full supply-supply links, full supply-demand links
```{r}
ggplot(notnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

# High supply (0.4), low demand (0.1)
```{r}
noneprox <- filter(out, p_supply == 0.1, p_demand == 0.1, is.na(ee_thres), es_thresh == 20)
nonenot <- filter(out, p_supply == 0.1, p_demand == 0.1, is.na(ee_thres), es_thresh == 100)
proxprox <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 20, es_thresh == 20)
proxnot <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 20, es_thresh == 100)
notnot <- filter(out, p_supply == 0.1, p_demand == 0.1, ee_thres == 100, es_thresh == 100)
```


## No supply-supply links, proximal supply-demand links
```{r}
ggplot(noneprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## No supply-supply links, full supply-demand links
```{r}
ggplot(nonenot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, proximal supply-demand links
```{r}
ggplot(proxprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, full supply-demand links
```{r}
ggplot(proxnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## Full supply-supply links, full supply-demand links
```{r}
ggplot(notnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

# High supply (0.4), high demand (0.4)

```{r}
noneprox <- filter(out, p_supply == 0.4, p_demand == 0.4, is.na(ee_thres), es_thresh == 20)
nonenot <- filter(out, p_supply == 0.4, p_demand == 0.4, is.na(ee_thres), es_thresh == 100)
proxprox <- filter(out, p_supply == 0.4, p_demand == 0.4, ee_thres == 20, es_thresh == 20)
proxnot <- filter(out, p_supply == 0.4, p_demand == 0.4, ee_thres == 20, es_thresh == 100)
notnot <- filter(out, p_supply == 0.4, p_demand == 0.4, ee_thres == 100, es_thresh == 100)
```


## No supply-supply links, proximal supply-demand links
```{r}
ggplot(noneprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## No supply-supply links, full supply-demand links
```{r}
ggplot(nonenot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, proximal supply-demand links
```{r}
ggplot(proxprox, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```

## Proximal supply-supply links, full supply-demand links
```{r}
ggplot(proxnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```


## Full supply-supply links, full supply-demand links
```{r}
ggplot(notnot, aes(x = f_supply, y = f_demand, fill = benefit_mean)) + 
  geom_tile() + 
  scale_fill_viridis_c() + 
  facet_grid(rival ~ inter)
```